\vspace{\baselineskip} The population of long-period transiting exoplanets \vspace{-2\baselineskip}

### 2016-09-19 document/ms.tex
comment about Clanton comparison between stellar types

\response{%
\citet{Clanton:2016} studied the occurrence rate of long-period giant planets
orbiting M dwarfs by combining results from radial velocity, microlensing, and
direct imaging surveys.
In the period and mass range $10^3-10^4\unit{days}$ and $10-10^4\,M_\oplus$,
they find a mean occurrence rate density of
\begin{eqnarray}
\frac{\dd^2 N}{\dd\ln M\,\dd\ln P} &=& 0.023
\end{eqnarray}
% \begin{eqnarray}
% \frac{\dd^2 N}{\dd\ln M\,\dd\ln P} &\lesssim& 0.013
% \end{eqnarray}
per M dwarf with large uncertainty.}
This result is slightly lower than our estimated rate for a similar range of
masses and periods but around G/K dwarfs.
This difference is consistent with previous results that cooler stars host
fewer long-period giant planets \citep[for example][]{Cumming:2008}.

>>>>

\response{%
\citet{Clanton:2016} studied the occurrence rate of long-period giant planets
orbiting M dwarfs by combining results from radial velocity, microlensing, and
direct imaging surveys.
In the period and mass range $10^3-10^4\unit{days}$ and $10-10^4\,M_\oplus$,
they find a mean occurrence rate density of
\begin{eqnarray}
\frac{\dd^2 N}{\dd\ln M\,\dd\ln P} &=& 0.023
\end{eqnarray}
% \begin{eqnarray}
% \frac{\dd^2 N}{\dd\ln M\,\dd\ln P} &\lesssim& 0.013
% \end{eqnarray}
per M dwarf with large uncertainty.}
This result is slightly lower than our estimated rate for a similar range of
masses and periods but around G/K dwarfs.
\response{%
This difference is consistent with previous results that cooler stars host
fewer long-period giant planets \citep[for example][]{Cumming:2008,
Clanton:2016}.
}
